\renewcommand{\abstractname}{Acknowledgements}
  % Discovered this functionality here: https://tex.stackexchange.com/a/82994
\abstract{
  
  I feel incredibly blessed that I have many people to thank for their support and help through the years I've spent working on this thesis.

  My thanks begin by going to my supervisors, Ivan Graham and Euan Spence. Ivan---thank you so much for all the support you've given me throughout my mathematical career, from being my personal tutor as an undergraduate, through supervising my undergraduate project, and now supervising this thesis. I've appreciated your honesty, the way you strive for excellence, and the way you've shown me that simple examples can often illuminate bigger mathematical truths. Euan---thank you for pushing me hard throughout my PhD, for forcing me to read Krantz and Higham, and for making me into (I hope) a much better writer and mathematician. Thank you also for generously funding me to travel to lots of conferences, for making those conferences a lot of fun, and for introducing me to lots of the `waves' community. Both---thank you for your pastoral support, especially through the more demanding parts of this PhD; I truly feel that I have had one of the best supervisory teams.

  There are lots of people to thank in the Department of Mathematical Sciences at the University of Bath; all of the SAMBa team past and present---Susie, Jess, Anna, Andreas, Paul, and many others---thank you for building a centre that is a fun place to study, and a great place to learn. My thanks also go to the Numerical Analysis group, for being a great blend of a friendly bunch of people who are also a stimulating group in which to do research.

  There are also numerous individuals to thank from Bath---Kieran Jarrett helped me get my head around measure theory for \cref{chap:stochastic}, Tony Shardlow gave us really helpful feedback on that same chapter. Tom Finn and Dan Ng helped me understand stopping times, and if Federico Cornalba hadn't discovered \cref{ex:federico}, then \cref{chap:stochastic} may never have been written! I've also been blessed with numerous office mates who have provided both stimulating conversation and welcome distraction (mathematical or otherwise); my thanks in particulat go to Aoibheann Brady, Matt Durey, Matt Parkinson, and Kate Powers.

  A special thanks goes to Will Saunders and Jack Betteridge, for putting up with my endless programming questions, often spending lots of their own time fixing my code, and convincing me to use version control and write tests for my code. A special thanks goes to Jack for being my Student-Led-Symposium-organising partner-in-crime and SAMBa-numerical-analysis-friend. 

  Looking at the wider academic community, I want to thank Rob Scheichl and Ralf Hiptmair for examining my thesis. Rob---thank you for lots of probing yet supportive questions and comments throughout my PhD and during my viva. Ralf---thank you for taking the time to read and examine my thesis, and for your very generous hospitality when I travelled to Z\"urich for my viva. My thanks also go to Stefan Sauter, Nilima Nigam and Th\'eophile Chaumont-Frelet, for their suggestions which led to me proving the weaker-norm bounds in \cref{sec:weaknorm}. I'm also very grateful to the Firedrake team for building the Firedrake software (without which, I wouldn't have been able to do all the numerical experiments in this thesis) and for very patiently answering my questions when I got stuck.
  
I'm also very blessed to have many people outside of mathematics who love me, support me, and tell me when I need to stop doing maths. A huge thanks should go to everyone at my church, St Bart's Bath, but especially to our very dear friends Will, Hannah, Emma, and Rich. Thank you all for lots of fun, laughter, love, support, and prayers. I'm also phenominally grateful to my parents; Mum and Dad, thank you for pushing me to do my best when I was younger, but more than that, thank you for your love, care, support, and prayers for us in many, many ways, over many, many years. To my sister Anwen and brother-in-law Paul, thank you both for your friendships, companionship and love over the years, I'm incredible grateful. Also, Paul, thank you very much for helping me with the design of this thesis, so that it looks good!

Above else, my thanks go to God. He is the incredible Trinity who has created me, has created mathematics and has enabled me to spend my time thinking about and wrestling with His creation. But more than that, L\textsc{ord}, thank You for revealing Yourself in the Bible, Father, thank you for choosing me before the foundation of the world, not because of anything I have done, but because You love me. Jesus, thank You for being incarnate as a man, and loving me so much that You would die on the cross for me, taking all the punishment and pain that I deserve as a sinner. Holy Spirit, thank You for dwelling within me, and reassuring me that I have the hope of a glorious future with You. L\textsc{ord}, Your love for me is beyond compare.
\thispagestyle{plain} % Found in https://tex.stackexchange.com/a/16347

And lastly, but by no means leastly, my thanks go to my wife, Rebecca. Reb, when we married I had already commited to studying for this PhD, and you have been such a wonderful support throughout it all. You've loved me dearly, supported and cared for me when I've needed it, persuaded me to keep going when I've wanted to give up, prayed for me, and had the wisdom to tell me when I should keep working and when I should stop for the evening. I don't think I'd have got here without you. And as I finish this thesis on our fourth wedding anniversary, I'm reminded again of how blessed I am to be loved by you.

\

\

\begin{center}
  {\it Rebecca, this thesis is dedicated to you.}
  \end{center}
}
