\section{Summary and future work}

\subsection{Summary}
In this \lcnamecref{chap:stochastic} we proved existence, uniqueness, and a $k$-independent a priori bound for the Helmholtz equation in random media under a $k$-independent nontrapping condition. In particular:
\bit
\item In \cref{sec:hh-results}  we gave sufficient conditions for (i) the equivalence of three different formulations of the Helmholtz equation in random media, (ii) existence and uniqueness of a solution, and (iii) a $k$-independent a priori bound on the solution.
  \item In \cref{sec:general} in an abstract setting we gave three different formulations of linear spatial stochastic PDEs, along with abstract sufficient conditions for (i) the equivalence of these formulations, (ii) existence and uniqueness of a solution, and (iii) an a priori bound on the solution. These abstract conditions were then applied to the Helmholtz equation.
\eit

\subsection{Future work}
There are several possibilities for applying and extending the results in this \lcnamecref{chap:stochastic}:
\bit
\item Applying the abstract results in \cref{sec:general} to other linear spatial stochastic PDEs, especially those whose standard variational formulations are not coercive, similar to the Helmholtz equation. One such example would be the time-harmonic Maxwell's equations, which are closely related to the Helmholtz equation, see the discussion in \cref{sec:motivapp}.
\item Extending the abstract results in \cref{sec:general} to cover coefficients that are not bounded almost surely; this extension should be straightforward, as the proofs in \cref{sec:genproof} are based on those in \cite{Gi:10,MuSt:11}, which treat coefficients that are not bounded almost surely.
  \item Attempting to extend the abstract results in \cref{sec:general} to nonlinear spatial stochastic PDEs. We expect this possibility would require substantially adapting the ideas and proofs in \cref{sec:general,sec:genproof} to the nonlinear case. However, if possible it would potentially allow one to prove well-posedness results for certain classes of nonlinear spatial stochastic PDEs.
\eit
